% Siconos-Doc version 3.0.0, Copyright INRIA 2005-2008.
% Siconos is a program dedicated to modeling, simulation and control
% of non smooth dynamical systems.	
% Siconos is a free software; you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation; either version 2 of the License, or
% (at your option) any later version.
% Siconos is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Siconos; if not, write to the Free Software
% Foundation, Inc., 51 Franklin St, Fifth Floor, Boston, MA  02110-1301  USA
%
% Contact: Vincent ACARY vincent.acary@inrialpes.fr 
%/
\documentclass[10pt]{article}
\input{../macro.tex}
\usepackage{psfrag}
\usepackage{fancyhdr}
\usepackage{subfigure}
%\renewcommand{\baselinestretch}{1.2}
\textheight 23cm
\textwidth 16cm
\topmargin 0cm
%\evensidemargin 0cm
\oddsidemargin 0cm
\evensidemargin 0cm
\usepackage{layout}
\usepackage{mathpple}
\usepackage[T1]{fontenc}
%\usepackage{array}
\makeatletter
\renewcommand\bibsection{\paragraph{References
     \@mkboth{\MakeUppercase{\bibname}}{\MakeUppercase{\bibname}}}}
\makeatother
%% style des entetes et des pieds de page
\fancyhf{} % nettoie le entetes et les pieds
\fancyhead[L]{}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}%
\begin{document}
\thispagestyle{empty}
\title{OneStepIntegrator and derived classes.}
\author{F. P\'erignon}

\date{For Kernel version 3.0.0 \\
 \today}
\maketitle

\pagestyle{fancy}

\section{Introduction}
This document is only a sequel of notes and remarks on the way OneStepIntegrators are implemented in Siconos.\\
It has to be completed, reviewed, reorganized etc etc for a future Developpers'Guide. \\
See also documentation in Doc/User/OneStepIntegrator for a description of various OSI.

\section{Class Diagram}

\section{Misc}

OSI review for consistency between Lsodar and Moreau:
\begin{itemize}
\item add set of DynamicalSystem*
\item add set of Interaction* 
\item add link to strategy that owns the OSI
\item remove td object in OSI -> future: replace it by a set of td (one per ds)
\item add strat in constructors arg list
\end{itemize}


osi -> strat -> Model -> nsds -> topology \\
osi -> strat -> timeDiscretisation \\

let a timeDiscretisation object in the OSI? set of td (one per ds)? \\
create a class of object that corresponds to DS on the simulation side ? \\
will contain the DS, its discretization, theta for Moreau ... ? \\ 
Allow setStrategyPtr operation? Warning: need reinitialisation. \\


Required input by user: \\
\begin{itemize}
\item list of DS or list of Interactions ? 
\item pointer to strategy
\item ...
\end{itemize}

\section{Construction}

Each constructor must:

\begin{itemize}
\item
\end{itemize}

\subsection{Moreau}

Two maps: one for W, and one for theta. To each DS corresponds a theta and a W. \\
Strategy arg in each constructor.

\bf{Required data:}\\

\bf{Optional:}\\

\bf{Always allocated in constructor:} \\

Warning: default constructor is always private or protected and apart from the others and previous rules or remarks do not always apply to it. 

\subsection{Lsodar}

\bf{Required data:}\\

\bf{Optional:}\\

\bf{Always allocated in constructor:} \\

\end{document}
