
This part will explain error messages which may appears during the execution of the platform.
There are 4 differents kind of exception : XML Exception, Siconos Matrix / Vector Exception, Shared Library Exception and Runtime Exception.
Each exception is accompanied by a message which explain the cause of the error and where it appears.
\\
\textit{
Remark~: It is possible that an error occurred just after the launch of the platform. Its appears when you try to run the platform without the script file "siconos", and your SICONOSPATH environment variable is not set. Just set this variable to fix this problem using "source siconos.csh"}

\section{XML Exception}
This exception is thrown when an error occurred in the \ac{xml} part of the platform. The error message is~: \\

\begin{minipage}{\textwidth}
\small{\textsf{XML Exception : ...}}\\
\end{minipage}
followed by a description of this error.
In general, the cause is a malformed \ac{xml} file or \ac{xml} schema.
Verify if these files exist and if they are well formed.

\section{Siconos Matrix / Vector Exception}
This exception is thrown when an error occurred in a Siconos Vector or a Siconos Matrix. The error message is~: \\

\begin{minipage}{\textwidth}
\small{\textsf{Siconos Vector Exception : ...}}\\
\end{minipage}
or ~: \\

\begin{minipage}{\textwidth}
\small{\textsf{Siconos Matrix Exception : ...}}\\
\end{minipage}
followed by a description of this error. The probable source of exception is a mathematic error (division by 0, ...), an index out of range or a Matrix / Vector file not found.


\section{Siconos Memory Exception}
This exception appears when an error occured in a SiconosMemory of the platform. The error message is~: \\
\begin{minipage}{\textwidth}
\small{\textsf{SiconosMemory Exception : ...}}\\
\end{minipage}
followed by a description of this error. This exception is throw when you try to add a memory vector whereas the memory is already full, when you try  to add a vector which size
is greater than the defined size for the memories, \dots


\section{Shared Library Exception}
This exception is thrown when an error occurred when trying to load a plugin. The error message is~: \\

\begin{minipage}{\textwidth}
\small{\textsf{Shared Library Exception : ...}}\\
\end{minipage}
followed by a description of this error. An error like this may occurred when a plugin is not found (pay attention to the \verb+LD_LIBRARY_PATH+ variable), or a function doesn't exist in a plugin.

\section{Runtime Exception}
This exception appears when an error occured during execution of the platform. The error message is~: \\

\begin{minipage}{\textwidth}
\small{\textsf{Runtime Exception : ...}}\\
\end{minipage}
followed by a description of this error. This exception is throw when you try to access to a no allocated pointer, to construct an object with bad parameters, \dots
