

The Design Document documentation of the platform is gorganised as follows :
 \begin{enumerate}
  \item  The \acf{qpdoc}
    \begin{itemize}
    \item Scope: The overall project
    \item Purpose:  The purpose of the \ac{qpdoc} Document is to check that the project is consisten
t with standards and plans which are defined below. As it is recommended (see be
llow) by the ESA software engineering standards to small software projects, the 
Quality Plan combines the following documents for small projects :
\begin{itemize}
\item The software Project Management Plan.
\item The software Configuration Management Plan.
\item The software Verification and Validation Plan.
%\item The software Quality Assurance. 
\end{itemize}

    \end{itemize}
  \item  The \acf{srd}
    \begin{itemize}
    \item Scope: The \ac{kernel} and \ac{imse} module
    \item Purpose:The \ac{srd} is a contractual document which aims to define precisely the software to realize. It describes functionalities and characteristics of the product and constraints of development and exploitation. It is addressed to users and software framework builders. 

    \end{itemize}
  \item  The \acf{esd}
    \begin{itemize}
    \item Scope: The \ac{kernel} and \ac{imse} module
    \item Purpose: The purpose of the \ac{esd} is to define the users requirements for the external user interfaces.
    \end{itemize}
  \item  The Architectural Design Document for the Kernel module (Kernel/ADD)
     \begin{itemize}
    \item Scope:  The \ac{kernel}
    \item Purpose: The \ac{add} is a document which aims to define the software architecture of the \ac{siconos}. This architecture relies on the specifications of the \ac{srd} and on the external specifications of the \ac{esd}.
The \ac{add} defines and describes the design of the system, in a manner that allows to elaborate it in details progressively. It will be used by the Project Manager to share out the detailed conception and programming in work packages.

    \end{itemize}
  \item  The \acf{ddd}
    \begin{itemize}
    \item Scope:  The \ac{kernel}
    \item Purpose:The \ac{ddd} aims to specify completely the data structures of~\ac{siconos}. This document relies on the global architecture designed in the \ac{add}. It consists essentially in a class-diagram and a set of constraints on it to eliminate most of its ambiguities. Implementation choices will also be explained and justified here. 
    \end{itemize}
  \item  The \acf{ssd} 
  \begin{itemize}
    \item Scope: The \ac{numerics}
    \item Purpose:The purpose of the Software Specification Document is to define the user and software requirements, and the architecture design of \ac{siconos}/Numerics. The \ac{ssd} is a contractual document which aims to define precisely the software to realize. It describes functionalities and characteristics of the product and constraints of development and exploitation. It is addressed to users and software framework builders. 
    \end{itemize}
  \item  \acf{dddnumerics} 
    \begin{itemize}
    \item Scope: The \ac{numerics}
    \item Purpose: The purpose of the Detailled Design Document is to specify completely the data structure of \ac{numerics}. It relies on the \ac{ssd} and its Architecture Design chapters.
    \end{itemize}  
  \item \acf{sum}
  \item \acf{sumnumerics}
  \item \acf{cds}
  \item \acf{tm}
  \item  A document entitled ``Guidelines for  authors'' for editing ``Templates'' and ``Benchmarks''.
 \end{enumerate}