\section{First Increment Production - Integration tests report}
The XML input file is complete, that's to say that all the objects of the formalization, solving strategy and XML management modules will
be used.

\subsection{Report of the communication tests between strategy and formalizatio modules}
The appendix \ref{siconos} shows the unfolding of the loading and the saving of data. At the end of the filling of the platform's data,
we can see the communication between OneStepIntegrator and DynamicalSystem, and between OneStepNSProblem and Interaction, because the
OneStepIntegrator and OneStepNSProblem objectshave written in the log file the number identifying the objects linked to them.

\subsubsection{Result log of platform's launching and saving}
\label{siconos}
\verbatiminput{siconos.exec}

\newpage
\subsection{Report of the communication tests between the XML management module and the remainder of the platform}
The appendices \ref{siconos} and \ref{xmltest} show the data transmitted during the reading of the XML input file. We can see that the
data are identical, so the information sent are correctly received.

\subsubsection{XML input file}
\label{xmltest}
\verbatiminput{xml_test.xml}

\newpage
\subsection{Report of the communication tests between the platform and the XML management module}
The appendices \ref{siconos} and \ref{xmlsave} show the data transmitted during the saving of the platform's data into an XML output
file. While comparing the output data to the original ones, we can see that data have been well saved.

\subsubsection{XML output file}
\label{xmlsave}
\verbatiminput{xml_save.xml}

\newpage
\subsection{Report of the communication tests between the platform and the plugins}
The appendices \ref{plugin} shows that the call of plugins' functions is well done. Each plugin's function appears in the log file when
the specified function is called by the pletform.

\subsubsection{Result log of plugins' integration}
\label{plugin}
\verbatiminput{plugin.exec}
