\section{Purpose of this document}
\label{Sec:QP-Purpose-Scope}
The purpose of the \ac{qpdoc} Document is to check that the project is consistent with standards and plans which are defined below. As it is recommended (see bellow) by the ESA software engineering standards to small software projects, the Quality Plan combines the following documents for small projects :
\begin{itemize}
\item The software Project Management Plan.
\item The software Configuration Management Plan.
\item The software Verification and Validation Plan.
%\item The software Quality Assurance. 
\end{itemize}



%% \section{Scope}
%% \label{Sec:ADD-Scope}




%% To be written



\section{References}
\label{Sec:ADD-References}
\begin{itemize}
\item \textbf{"Guide to applying the ESA software engineering standards to small software projects. ", BSSC(96)2, \ac{esa} 1996},
\item \textbf{"Guide to the  software project management ", PSS-05-08, \ac{esa} 1995},
\item \textbf{"Guide to the  software configuration management", PSS-05-09, \ac{esa} 1995},
\item \textbf{"Guide to the  software verification and validation", PSS-05-10, \ac{esa} 1995},
\item \textbf{"Guide to the  software quality assurance", PSS-05-11, \ac{esa} 1995},
\item \ac{urd}
\item \ac{srd}
\item \ac{add}
\item \ac{ddd}
\item \ac{esd}
\item \ac{cds}
\item \ac{ssd}
  % \item \ac{dad}
  % \item \ac{paql}
  % \item \ac{pdl}
\end{itemize}

\section{Overview}

%\begin{ndr}
%  To Be Reviewed
%\end{ndr}
The Chapter \ref{Sec:QP-PMP} describes the software Project Management Plan, i.e., the process of planning, organizing, staffing, monitoring,
controlling and leading a software project.\\
The Chapter \ref{Sec:QP-CMP} explains the major features of the Configuration Management Plan.
The purpose of the software configuration management is to plan, organize, control and coordinate the identification, storage and change
of software through development, integration and transfer.\\
The Chapter \ref{Sec:QP-VVP} contains the Verification and Validation Plan which aims checking the specifications.\\
The Chapter \ref{Sec:QP-PRUT} presents the Unitary tests which are the way to ensure that low level functions are reliable. The plans of integration tests are described in the Chapter~\ref{Sec:QP-PRIT} and the acceptance tests in the Chapter~\ref{Sec:QP-PRAT}


\section{Evolution of the document}

This document will  be improved all along the process of design and development. Particularly, the various management plans will be completed, detailed and adapted to the design and development processes.


 Updated versions may be found on \texttt{http://siconos.inrialpes.fr/software}  