\section{Increment 1}

\subsection{Introduction}
At first, we must know the software is a scientific computation platform. It's compouned of two main parts. The first part is made of a
formalization module and a solving strategy one. This part is the intelligence of the software. In front of that, the second part which
manage XML data, has the same structure that the first part.\\
The selected integration strategy is a progressive integration by subsystem, where the subsystems were these defined during the
conception. The first subsystems are the formalization  and the solving strategy modules of the platform. Then all the XML management
module has been integrated to the growing platform. The plugins were added once the platform was built.

This document aims to present the tests done to validate the integration of the platform. The modules concerned are the formalization,
the solving strategy and the XML management.\\
This plan will highlight the communications between the various modules, to check the good unfolding of the communications.\\
In this document you will find two main parts :
\begin{itemize}
	\item a File part, which defines the development strategy used and the satisfaction criteria.
	\item a Result part, which explain the results of the tests and analyze them.
\end{itemize}

\begin{ndr}
thids document must be continued with the integration of SICONOS/Numerics !
\end{ndr}


\subsection{Tests file}
This chapter defines in detail, all the tests used, the adopted development strategy, and the satisfaction criteria.

\subsubsection{Introduction}
These integration tests are done during the development of each module within the assigned time. They began when the API was complete and
when the development was enough advanced.

\subsubsection{Testing strategy}
The tests are built to check all the links between modules and that the communications are well done.

\subsubsection{Satisfaction criterions}
The integration tests are validated by the person in charge for the tests and for quality.
They must clearly show that the communication between modules are established, and the good and complete unfolding of all the tests.
The test suite must test all the ways of communication between the modules. The XML test file is complete and exhaustive for all the
objects the platform manages.

\subsubsection{Development of the tests}
%\subsubsection{Communication tests between strategy an the formalization}
\paragraph{Communication tests between strategy an the formalization}
(Work breakdown structure.3611)\\
With this test, we verify that the communications between each OneStepIntegrator and his DynamicalSystem are well established, and like
that each OneStepNSProblem is well associated with his Interactions. This link is one-way, so we will check thatthe objects of the
solving strategy module can display the name of the formalization module's object which is associated to it.

%\subsubsection{Communication tests between the XML management module and the remainder of the platform}
\paragraph{Communication tests between the XML management module and the remainder of the platform}
(Work breakdown structure.3611.1, 3611.2, 3611.3)\\
In this test, we check that the reading of an XML inpt file will create the link between the XML management module's objects and the
formalization and solving strategy modules' objects. Indeed, when an XML input file is read, all the XML objects are created, and then,
the other object of the platform must be created.\\
The basement of the platform id the "Model" object type. It is a Model that will launch the reading of the XML input file. When the XML
objects are created, the Model will begin to create and link the formalization ad strategy objects to the XML objects.\\
We ensure oneself of the exactitude of the result by checking the called functions during the unfolding of the test. All the methods
called will print to the screen their name in a log file, so it is easy to see what happen. The resulting data of this test consists in a serie of
method call that we can compare with the XML input data.

%\subsubsection{Communication tests between the plateform and the XML management module}
\paragraph{Communication tests between the plateform and the XML management module}
(Work breakdown structure.3611.3)\\
In this test, we check that the communications between each object of the platform are well done with the XML object associated to it.\\
In this way of communication, it correspond to the save of the platform data to an XML file.\\
We ensure oneself of the exactitude of the result by checking the method called in the log file. Moreover, the XML output file must be
similar to the input file because no computations have been made with the data.

%\subsubsection{Communication tests between the platform and these plugins}
\paragraph{Communication tests between the platform and these plugins}
(Work breakdown structure.3611.4)\\
This test must show tht the platform use the methods given with the plugins.\\
To do that, we check the log file where the functions of the plugins must have made specific outputs.


%======report to put somewhere else=============

%\section{Integration tests report}
%The XML input fileis complete, that's to say that all the objects of the formalization, solving strategy and XML management modules will
%be used.

%\subsection{Report of the communication tests between strategy and formalizatio modules}
%The appendix \ref{siconos} shows the unfolding of the loading and the saving of data. At the end of the filling of the platform's data,
%we can see the communication between OneStepIntegrator and DynamicalSystem, and between OneStepNSProblem and Interaction, because the
%OneStepIntegrator and OneStepNSProblem objectshave written in the log file the number identifying the objects linked to them.

%\subsection{Report of the communication tests between the XML management module and the remainder of the platform}
%The appendices \ref{siconos} and \ref{xmltest} show the data transmitted during the reading of the XML input file. We can see that the
%data are identical, so the information sent are correctly received.

%\subsection{Report of the communication tests between the platform and the XML management module}
%The appendices \ref{siconos} and \ref{xmlsave} show the data transmitted during the saving of the platform's data into an XML output
%file. While comparing the output data to the original ones, we can see that data have been well saved.

%\subsection{Report of the communication tests between the platform and the plugins}
%The appendices \ref{plugin} shows that the call of plugins' functions is well done. Each plugin's function appears in the log file when
%the specified function is called by the pletform.


%===================
%\appendix
%\newpage
%\chapter{Result log of platform's launching and saving}
%\label{siconos}
%\verbatiminput{siconos.exec}

%\newpage
%\chapter{XML input file}
%\label{xmltest}
%\verbatiminput{xml_test.xml}

%\newpage
%\chapter{XML output file}
%\label{xmlsave}
%\verbatiminput{xml_save.xml}

%\newpage
%\chapter{Result log of plugins' integration}
%\label{plugin}
%\verbatiminput{plugin.exec}
