% Siconos-Doc version 2.1.1, Copyright INRIA 2005-2007.
% Siconos is a program dedicated to modeling, simulation and control
% of non smooth dynamical systems.	
% Siconos is a free software; you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation; either version 2 of the License, or
% (at your option) any later version.
% Siconos is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Siconos; if not, write to the Free Software
% Foundation, Inc., 51 Franklin St, Fifth Floor, Boston, MA  02110-1301  USA
%
% Contact: Vincent ACARY vincent.acary@inrialpes.fr 
%/
\documentclass[10pt]{article}
\input{../macro.tex}
\usepackage{psfrag}
\usepackage{fancyhdr}
\usepackage{subfigure}
%\renewcommand{\baselinestretch}{1.2}
\textheight 23cm
\textwidth 16cm
\topmargin 0cm
%\evensidemargin 0cm
\oddsidemargin 0cm
\evensidemargin 0cm
\usepackage{layout}
\usepackage{mathpple}
\usepackage[T1]{fontenc}
%\usepackage{array}
\makeatletter
\renewcommand\bibsection{\paragraph{References
     \@mkboth{\MakeUppercase{\bibname}}{\MakeUppercase{\bibname}}}}
\makeatother
%% style des entetes et des pieds de page
\fancyhf{} % nettoie le entetes et les pieds
\fancyhead[L]{}
\fancyhead[R]{\thepage}
\fancyfoot[C]{}%
\begin{document}
\thispagestyle{empty}
\title{Notes on the Non Smooth Dynamical System construction}
\author{F. P\'erignon}

\date{For Kernel version 2.1.1 \\
 \today}
\maketitle

\pagestyle{fancy}

\section{Introduction}

\section{Class Diagram}

\section{Description}

Objects must be constructed in the following order: 
\bei
\item DynamicalSystems
\item NonSmoothLaw: depends on nothing
\item Relation: no link with an interaction during construction, this will be done during initialization. 
\item Interaction: default constructor is private and copy is forbidden. Two constructors: xml and from data. Required data are a DSSet, a NonSmoothLaw and
a Relation (+ dim of the Interaction and a number). \\
Interaction has an initialize function which allocates memory for y and lambda, links correctly the relation and initializes it .... This function is called at the 
end of the constructor. That may be better to call it in simulation->initialize? Pb: xml constructor needs memory allocation for y and lambda if they are
provided in the input xml file. 
\item NonSmoothDynamicalSystem: default is private, copy fobidden. Two constructors: xml and from data. Required data are the DSSet and the InteractionsSet.
The topology is declared and constructed (but empty) during constructor call of the nsds, but initialize in the Simulation, this because it can not be initialize until the nsds has been fully described (ie this to allow user to add DS, Inter ...) at any time in the model, but before simulation initialization). 

\ei

\section{misc}

\bei 
\item no need to keep a number for Interactions? Only used in xml for OSI, to know which Interactions it holds.
\item pb: the number of saved derivatives for y and lambda in Interactions is set to 2. This must depends on the relative degree which is computes during
Simulation initialize and thus too late. It is so not available when memory is allocated (Interaction construction). Problem-> to be reviewed.
\ei 

\end{document}
